Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-22 paper.tex
Added new figure. Other minor edits
Edit/fix to figure and not using project name. Other small edits

\noindent It is estimated that almost half billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives. Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
%The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or
The work here presented is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone. The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of the moving camera with the body (i.e. arm, hand) of the user holding the smartphone. Schematically, the actuators used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, are replaced by a human. %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

The goal of the ActiVis system is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what is currently within view and what has been observed in the past. We trained a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action the agent (the guidance system in this case) takes when it finds itself within some state.

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
  \caption{The ActVis system layout and control loop. \todo{Explain the meanings of the symbols r, e, ... in the caption. Remove all direct references to ActiVis with more generic ``our project''.}}\label{fig:control-loop}
\end{figure}

@@

Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the ActiVis guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}. Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.

@@

\noindent The ActiVis project's goal is to deliver a stand-alone system that can guide a VI user to their destination with minimal user input or intervention. A complete system diagram is given is Figure~\ref{fig:control-loop}. The system design loop is similar to that of a classical control problem where a controller generates a control signal that drives a component towards some reference point. In this case, the reference signal, $r$, is the object the user wishes to find which is achieved by placing the target object within the camera's view. Therefore, the goal of the control block, $K$, is to generate guidance instructions, $u$ to drive the user along a search path towards the target object. Since we place a human in the control loop, we have an extra block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, that makes a new object observation. The new observation is then fed back to the loop and the error signal, $e$, is updated accordingly.

@@

\begin{table}
  \centering
  \caption{The reward functions for the MDP.\ }\label{tab:rewards}
  \begin{tabular}{ll}
    \toprule
    $r(s, s'), s\in\mathbf{S}$ & -1  \\ \midrule
    $r(n > n_{\max})$ & -10 \\ \midrule
    $r(v = true)$  & -10 \\ \midrule
    $r(o = o_{target})$ & 10000 \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}                      
  \centering                       
  \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
  \begin{tabular}{llc}
    \toprule
    \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
			      & Simulation & 99.7 \\ \midrule
    \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
			        & Simulation & 5.4 \\ \midrule
    Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\noindent It is estimated that almost half a billion people worldwide live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives. Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem.
%The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or
The work presented here is part of a project to assist the visually impaired (VI) navigate and find objects in unknown environments with the aid of a smartphone. The proposed system implements ideas from the field of active vision~\cite{Bajcsy2017}, but replaces the typical electro-mechanical actuators of the moving camera with the body (i.e.\ arm, hand) of the user holding the smartphone, as pictured in Figure~\ref{fig:system-use}. Schematically, the actuators used in a typical control loop, pictured in Figure~\ref{fig:control-loop}, are replaced by a human. %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

\begin{figure}
  \centering
  \begin{subfigure}
    \centering
    \includegraphics[width=0.38\textwidth]{figures/system_use.png}
    \caption{The system in use during an experiment. }\label{fig:system-use}
  \end{subfigure}
  \begin{subfigure}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/control_loop.png}
    \caption{The system layout and control loop. $r$ is the reference object, $e$ the error signal, $u$ and $u^*$ the original and interpreted control signals and $y$ is the current object observation. $K$, $H$ and $P$ are the control, human and sensor blocks respectively. }\label{fig:control-loop}
  \end{subfigure}
\end{figure}

The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what is currently within view and what has been observed in the past. We trained a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action the agent (the guidance system in this case) takes when it finds itself within some state.

@@

Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}. Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.

@@

\noindent This project's goal is to deliver a stand-alone system that can guide a VI user to their destination with minimal user input or intervention. A complete system diagram is given is Figure~\ref{fig:control-loop}. The system design loop is similar to that of a classical control problem where a controller generates a control signal that drives a component towards some reference point. In this case, the reference signal, $r$, is the object the user wishes to find which is achieved by placing the target object within the camera's view. Therefore, the goal of the control block, $K$, is to generate guidance instructions, $u$ to drive the user along a search path towards the target object. Since we place a human in the control loop, we have an extra block, $H$, that interprets $u$ and executes a physical action, $u^*$, that manipulates the sensor, $P$, that makes a new object observation. The new observation is then fed back to the loop and the error signal, $e$, is updated accordingly.

@@

\begin{table}
  \centering
  \caption{The reward functions for the MDP.\ }\label{tab:rewards}
  \begin{tabular}{cc}
    \toprule
    $r(s, s'), s\in\mathbf{S}$ & -1  \\ \midrule
    $r(n > n_{\max})$ & -10 \\ \midrule
    $r(v = true)$  & -10 \\ \midrule
    $r(o = o_{target})$ & 10000 \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}                      
  \centering                       
  \caption{The means and standard deviations for the entire participant population for the experiments and simulations.}\label{tab:results-summary}
  \begin{tabular}{ccc}
    \toprule
    \multirow{2}{*}{TAR [\%]} & Experiment & 82 $\pm$ 11  \\ 
			      & Simulation & 99.7 \\ \midrule
    \multirow{2}{*}{Num. Steps} & Experiment & 6.8 $\pm$ 5.1 \\ 
			        & Simulation & 5.4 \\ \midrule
    Time [s] & Experiment & 34 $\pm$ 23  \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}
